Exploratory_Analysis_Josh_Tobey

### 2025-12-05 Exploratory_Analysis_Josh_Tobey.Rmd
New plots and some preliminary model fitting

```{r}
library(tidyverse)
library(tidymodels)
library(dplyr)
library(knitr)

@@

```{r}
exploratory_df <- read_csv("RWAR_DOSING_clean.csv")
colnames(exploratory_df)
```

```{r}
ggplot(exploratory_df) +
  geom_point(aes(x = `Turbidity, NTU`,
                 y = `Temperature, deg C`,
                 color = `Temperature, deg C`)) +
  scale_color_gradient(low = 'yellow', high = 'green')
```

@@

```
```{r}
exploratory_df$Timestamp = mdy_hm(exploratory_df$Timestamp)
ggplot(exploratory_df, aes(x = Timestamp,
                           y = `pH, SU`,
                           color = `pH, SU`)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red')

@@

```{r}
unique(exploratory_df$`Conductivity, mS cm-1`)
```
```{r}
ggplot(exploratory_df) +
  geom_jitter(aes(x = `Turbidity, NTU`,
                 y = `Conductivity, mS cm-1`,
                 color = `Conductivity, mS cm-1`), width = 1, height = 3) +
  scale_color_gradient(low = 'skyblue', high = 'orange')

@@

>>>>

```{r}
library(tidyverse)
library(tidymodels)
library(dplyr)
library(knitr)
library(lubridate)

@@

```{r}
exploratory_df <- read_csv("RWAR_dosing_cleaned.csv")
colnames(exploratory_df)
```

```{r}
ggplot(exploratory_df) +
  geom_point(aes(x = mean_Turbidity,
                 y = mean_Temp,
                 color = mean_Temp)) +
  scale_color_gradient(low = 'yellow', high = 'green')
```

@@

```
```{r}
summary(exploratory_df)

@@

```{r}
exploratory_df$Timestamp = ymd(exploratory_df$Timestamp)
exploratory_df <- exploratory_df[order(exploratory_df$Timestamp), ]
ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red')

```
```{r}
exploratory_df$Timestamp <- ymd(exploratory_df$Timestamp)
exploratory_df <- exploratory_df[order(exploratory_df$Timestamp), ]
ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_Temp,
                           color = mean_Temp)) +
  geom_line() + 
  scale_color_gradient(low = 'yellow', high = 'green')

```
```{r}
library(patchwork)
plot1 <- ggplot(exploratory_df, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Average pH over Time")

plot2 <- ggplot(exploratory_df, aes(x = Timestamp,
                           y = Cationic.Polimer..mg.L,
                           color = Cationic.Polimer..mg.L)) +
  geom_line() + 
  scale_color_gradient(low = 'yellow', high = 'green') +
  theme_minimal() +
  ggtitle("Polymer Coagulant over Time")

plot1/plot2
```

```{r}
ggplot(exploratory_df) +
  geom_jitter(aes(x = mean_Turbidity,
                 y = mean_Conductivity,
                 color = mean_Conductivity), width = 1, height = 3) +
  scale_color_gradient(low = 'skyblue', high = 'orange')

@@

coagual
